Fractional Types

### 2016-12-17 typespp.tex
make fractional types pointed and use point to keep track of dependency
plan for end of sec 5 and sec 6

@@

>>>>

at end of previous section; add a new subsection explaining functor showing
equivalence of 1 and #p x 1/#p. Morita functor. Pullback condition. there is a
choice for eta but there is an extra condition that the choices are all
consistent. The big question is how to encode this global condition; side
effect; synchronization; etc. so naturally lead to pointed types and revise types

@@

Idea is to change the types to be of the form $\Sigma_{\overline{k}}\mathbb{T}$
where we keep track of the values (pointed types). When we take a product we
concatenate the two sequences of integers.
\[
(\textrm{Fractional Types})  \mathbb{T} ::=
  \Sigma_k\order{c} \alt \Sigma_k\iorder{c} \alt
  \Sigma_{\overline{j},\overline{k}}\mathbb{T}_1 \circledast \mathbb{T}_2
\]
